### 2014-02-25 paper/concrete.tex
More text.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

The operational semantics we have derived in the previous section
constitutes an abstract \emph{specification}: a semantics for which
non-interference is (obviously) true.  This specification can guide the
design of an information-flow calculus which would not be directly
derivable from our procedure, but is related to some such derivation.
For example, in our mini-ML language, the combined semantics requires
each thread to have a separate ML heap.  In an actual implementation, we
might like to only have a \emph{single} heap, with some restrictions to
enforce the illusion of separate heaps.  If these restrictions cause our
implementation semantics to behave in the same way as the specification
semantics (modulo some extra conditions), we might hope that we also
automatically achieve non-interference.

We can make this formal as follows: \Red{Define some notation}

@@

    Next, suppose we have a language $L'$ with machine states $|Q|$,
    evaluation relation $|.->|'$ and erasure function $e'$.  Given
    functions $f^{-1} : |C -> Q|$ and $f : |Q -> C|$ relating machine
    states between $L$ and $L'$, obeying the condition $f^{-1} \circ f =
    id$ and $f^{-1} \circ e' \circ f = e$.  Then to show termination sensitive non-interference for $L'$,
    it suffices to show that for every evaluation rule $|Q| |.->|' |Q'|$
    it is either the case that $f(|Q|) |.->| f(|Q'|)$ or that
    \ldots
\end{theorem}

\begin{proof}
Our proof proceeds along the same lines as a traditional TSNI proof,
we simply must show \Red{Lemma~1} holds for our language.  We proceed by induction
over reduction derivations in the first step.
\end{proof}

>>>>

The operational semantics we have derived in the previous section
constitutes an abstract \emph{specification}: a semantics for which
non-interference is (obviously) true.  This specification can guide the
design of an information-flow calculus which would not be directly
derivable from our procedure, but is related to some such derivation.
For example, in our mini-ML language, the combined semantics requires
each thread to have a separate ML heap.  In an actual implementation, we
might like to only have a single heap, but disallowing the
passing of references between threads.  This restriction maintains a
correspondence between the abstract multiple heaps and the concrete
single heap.  As long as we don't add any extra transitions which directly
leak secret data, we might hope that non-interference follows
immediately.

However, when proving termination-\emph{sensitive} non-interference, we
cannot allow an arbitrary restrictions.  Consider a trivial state
machine as shown in Figure~\ref{fig:trivial-sm}, whose second projection
is classified secret.  With all three transitions, this language
fulfills termination-sensitive noninterference.  Furthermore, if the
dashed line is removed, the language continues to satisfy TSNI.
However, if any solid line is removed, however, the language fails TSNI.
Only \emph{some} transitions may be removed safely.

\begin{figure}
    States: $(x,y)$ for $x,y \in \{0,1\}$ \\
    Erasure function: $f(x,y) = (x,\bullet)$

    \begin{center}\begin{tikzpicture}[node distance=2cm, auto]
        \node (A) {$(1,1)$};
        \node (B) [right of=A] {$(1,0)$};
        \node (C) [below of=A] {$(0,1)$};
        \node (D) [right of=C] {$(0,0)$};
        \draw[->] (A) to node {} (B);
        \draw[->] (C) to node {} (D);
        \draw[->, dashed] (B) to node {} (D);
    \end{tikzpicture}\end{center}

    \label{fig:trivial-sm}
    \caption{A trivial state machine}
\end{figure}

In order to capture the condition with which transitions may be removed
safely, we require a novel, stronger variant of termination-sensitive
noninterference:

\begin{lemma}[Erased-transition/transition simulation (ETTS)]
    For any state |C|, if |erase l C .-> delta|, then there exists a |C'| such that
    |erase l C' = delta| and |C .=> C'|.
\end{lemma}

Traditional TSNI is an easy corollary of this lemma.  Now we can state
the result:

@@

    Next, suppose we have a language $L'$ with machine states $|Q|$,
    evaluation relation $|.->|'$ and erasure function $e'$.  Given
    functions $f^{-1} : |C -> Q|$ and $f : |Q -> C|$ relating machine
    states between $L$ and $L'$, obeying the conditions:

    \begin{itemize}
        \item $f$ is functorial over $l$-equivalence: if
            $|Q1| \approx'_l |Q2|$ then $f(|Q1|) \approx_l f(|Q2|)$.
    \end{itemize}

    (Probably $f^{-1} \circ f =
    id$ and $f^{-1} \circ e' \circ f = e$)  Then to show termination sensitive non-interference for $L'$,
    it suffices to show that for every evaluation rule $|Q| |.->|' |Q'|$
    it is either the case that $f(|Q|) |.->| f(|Q'|)$ or that
    \ldots
\end{theorem}

\begin{proof}
Our proof proceeds along the same lines as a traditional TSNI proof,
we simply must show \Red{Lemma~1} holds for our language.  We proceed by induction
over reduction derivations in the first step.

We have $ts'_1 \approx_l ts'_2$ and would like to show $f(ts'_1) \approx_l f(ts'_2)$;
this can be seen by expanding the definition of
\end{proof}
